Time slice analyses

### 2017-11-01 analyses/02-time-slice-analyses.Rmd
Fix bins and source

## Load functions using source
# Need to fix this!
# source("../functions/simulations_fun.R")
```

@@

for (bins in seq_along(c(2, 5, 10, 15, 20))){
  output <- run.all.disparity(morphospace, tree, bins, FADLAD, inc.nodes = TRUE,
                              bootstraps = 100, = c(sum, variances), metric.name = sum_var){

>>>>

## Load functions using source
# Doesn't always work... Rmd problem?
source("../functions/simulations_fun.R")
```

@@

for (bins in c(2, 5, 10, 15, 20)){
  output <- run.all.disparity(morphospace, tree, bins, FADLAD, inc.nodes = TRUE,
                              bootstraps = 100, = c(sum, variances), metric.name = sum_var){
